\chapter{
    \textbf{References}
}
\begin{enumerate}[{[1].}]
    \item Mehmet Zeki Konyar, Serdar Solak, “Efficient data hiding method for videos based on adaptive inverted LSB332 and secure frame selection with enhanced Vigenere cipher”, in Journal of Information Security and Applications, 2021.
    \item Liu Yunxia, Liu Shuyang, Wang Yonghao, Zhao Hongguo, Liu Si, “Video steganography: A review” in Neurocomputing, 2019.
    \item Solak S, Altinisik U, “A new approach for steganography: bit shifting operation of encrypted data in LSB (SED-LSB)” in Int J Inform Technol 2019.
    \item Kar N, Mandal K, Bhattacharya B, “Improved chaos-based video steganography using DNA alphabets” in ICT Express, 2018.
    \item Farri E, Ayubi P, “A blind and robust video watermarking based on IWT and new 3D generalized chaotic sine map” in Nonlinear Dyn 2018.
    \item Eltahir ME, Kiah LM, Zaidan BB, “High rate video streaming steganography” in International conference on information management and engineering (ICIME ’09), 2009.
    \item Ding H, Tao R, Sun J, Liu J, Zhang F, Jiang X, Li J, “A compressed-domain robust video watermarking against recompression attack” in IEEE Access, 2021.
    \item Chen L, Zhao J, “Contourlet-based image and video watermarking robust to geometric attacks and compressions” in Multimed Tools Appl, 2018.
    \item Solak S, “High embedding capacity data hiding technique based on EMSD and LSB substitution algorithms” in IEEE Access, 2020.
    \item Mohammadi S, “A chaos- based video watermarking in wavelet domain” in Ciˆencia e Natura, 2015.
\end{enumerate}